Predictive Regressions with Persistent Regressors:\\ Monte Carlo evidence for the Bonferroni Q-test

### 2019-09-14 paper.tex
FIX typos

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. \citet{elliott1994inference} find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, \citet{campbell2006efficient} develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in section $\ref{Infeasible tests}$. This section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by \citet{campbell2006efficient}. Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in section $\ref{implementation}$. First, Monte Carlo evidence of \citet{campbell2006efficient} is scrutinized and replicated in section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovation variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in section $\ref{Empirical Results}$. Finally, section $\ref{conclusion}$ concludes.

@@

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A naïve approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being unacceptably larger than nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in section $\ref{pretest}$.

@@

\subsection{A pretest}
\label{pretest}
From equation ($\ref{lua_t}$) it's easy to see that if $\delta = 0$, the nuisance term $\delta \frac{\tau_{c}}{\kappa_{c}}$ vanishes and the t-statistic collapses to the standard normal random variable $Z$. It therefore makes sense to test whether $\delta$ is different from zero. If it isn't, one can infer that the t-statistic is approximately standard normal and inference based on it is valid. This, however, is not the only condition in which there is no size distortion. \citet{phillips1987towards} shows that if $x_{t}$ is not persistent, $\tau_{c} / \kappa_{c}$ converges to a different standard normal random variable $Z^{\star}$. Hence the t-statistic, as a sum of two independent standard normal random variables, is likewise standard normal.

@@

Implementing the feasible Q-test, first $\hat{\beta}$ and its standard error $\operatorname{SE}(\widehat{\beta})$ are obtained by OLS estimation of equation ($\ref{eqn:1}$). $x_{t}$ is written in its augmented Dickey-Fuller form
\begin{equation}
\Delta x_{t}=\tau+\theta x_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta x_{t-i}+e_{t},
\end{equation}
where $\psi_{i}=-\sum_{j=i}^{p-1} a_{j}$, $a(L)=L^{-1}[1-(1-\rho L) b(L)]$, and $\theta=(\rho-1) b(1)$. Estimation of $\widehat{\psi}_{i}(i=1, \ldots, p-1)$ is done via OLS where $p$ is either explicitly specified or estimated via the Bayesian information criterion [BIC].
With $\widehat{u}_{t}$ and $\widehat{e}_{t}$ being the residuals of regression (1) and (2), respectively,
\begin{align} \widehat{\sigma}_{u}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t}^{2} \\ \widehat{\sigma}_{e}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{e}_{t}^{2} \\ \widehat{\sigma}_{u e} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t} \widehat{e}_{t} \\ \widehat{\delta} &=\frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{u} \widehat{\sigma}_{e}} \\ \widehat{\omega}^{2}&=\widehat{\sigma}_{e}^{2} /\left(1-\sum_{i=1}^{p-1} \widehat{\psi}_{i}\right)^{2}
\end{align}
are then computed. OLS estimation of equation ($\ref{eqn:22}$) yields $\widehat{\rho}$ and its standard error $\mathrm{SE}(\widehat{\rho})$. The residual $\widehat{v}_{t}$ is used to compute 
\begin{equation}
\widehat{\sigma}_{v}^{2}=(T-2)^{-1} \sum_{t=1}^{T} \widehat{v}_{t}^{2}.
\end{equation} 
Now, to compute the DF-GLS statistic, $\left(x_{0}, x_{1}-\rho_{G L S} x_{0}, \ldots, x_{T}-\rho_{G L S} x_{T-1}\right)^{\prime}$ is regressed onto 
$\left(1,1-\rho_{G L S}, \ldots, 1-\rho_{G L S}\right)^{\prime}$ with $\rho_{G L S}=1-7 / T$. The coefficient $\mu_{G L S}$ is used to compute $\overline{x}_{t}=x_{t}-\mu_{G L S}$ which, in turn, is needed for the regression 
\begin{equation}
\Delta \overline{x}_{t}=\theta \overline{x}_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta \overline{x}_{t-i}+e_{t},
\end{equation} which is estimated with no intercept. Finally, the t-statistic for $\theta$ is computed. This is the DF-GLS statistic. To confirm that no error is conducted in this estimation procedure, the DF-GLS statistic thus obtained is compared to the implementation in the urca package of \citet{urca}.

@@

\section{Monte Carlo simulation}
This section, next to the out-of-sample results in section $\ref{Empirical Results}$, accommodates one of the main contributions of this paper.\footnote{All code generating the Monte Carlo results is available at https://github.com/jpwoeltjen/\\PersistentRegressors/tree/master/MonteCarlo.} First, Monte Carlo evidence of \citet{campbell2006efficient} is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in the form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of \citet{campbell2006efficient} with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by \citet{phillips2014confidence}, the feasible Q-test as derived in section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of \citet{campbell2005implementing}. Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood, the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

\citet{campbell2006efficient} evaluate the robustness of the Q-test under a fat-tailed distribution. In particular, they find finite-sample rejection probabilities to be unchanged from the Gaussian case when the innovations follow a Student t-distribution with five degrees of freedom. As shown by \citet{cavaliere2005unit}, unit root tests may be invalid under conditional heteroskedasticity. Assumptions in the form of equation ($\ref{eqn:covarst}$) imply validity of the Q-test under conditionally heteroskedastic innovations only if they are covariance stationary. 

@@

Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend)}
\label{tab:cst-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets, negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the conditional variance of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$, negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis, $\eta_{t}$ in equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%. For very large sample sizes of more than 1000 observations, a single spike of over-rejection is found when the GARCH process is very near nonstationarity. Otherwise, rejection rates are close to the nominal size.

@@

For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor, invalidating inference based on t-statistics, which otherwise would be statistically significant. Based on the Bonferroni Q-test, the null hypothesis of no predictability can be rejected at the 5\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively. 

@@

$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.

>>>>

\section{Introduction}
The question whether asset returns can be predicted with the help of observable variables is of great interest to financial institutions and the public as a whole. One of the most economically intuitive relationships exists between the price of a company's stock and the discounted earnings it will generate in the future. Since future earnings are not observable, current earnings or dividends or moving averages of them are often used as a proxy. To statistically test whether these variables are indeed predictive, one may test the significance of coefficients in a regression of the supposedly predictive variable onto equity market returns. The most straightforward way of doing this is via the t-test. \citet{elliott1994inference} find that this test has a nonstandard distribution under the null if the largest autoregressive root of the regressor is close to unity and the innovations of regressor and regressand are correlated. Given the presence of these nuisances, the t-test will lead to invalid inference. In this context, \citet{campbell2006efficient} develop a test that exploits information about the autoregressive root of the regressor and thus tries to overcome this issue. Section $\ref{regression}$ formalizes the regression setup and outlines the problem. Section $\ref{Derivation of the tests}$ explains the derivation of Campbell and Yogo's (2006) test. This is done by first considering optimal tests, albeit under unrealistic assumptions, in Section $\ref{Infeasible tests}$. This Section also establishes the conditions for a nonstandard distribution of the t-statistic. A pretest based on these conditions is described in Section $\ref{pretest}$. Section $\ref{Making the Q-test feasible}$ details the use of Bonferroni's inequality in making the test feasible.  The test is further generalized to more realistic assumptions in Section $\ref{implementation}$ and its mathematical implementation is described. Section $\ref{power}$ summarizes the power advantages of the test found by \citet{campbell2006efficient}. Section $\ref{Monte Carlo simulation}$ proceeds with evaluating finite-sample rejection rates of the feasible Q-test under various innovation distributions and violations of assumptions made in Section $\ref{implementation}$. First, Monte Carlo evidence of \citet{campbell2006efficient} is scrutinized and replicated in Section $\ref{Simulation with Gaussian innovations}$. Section $\ref{Simulation with weakly persistent regressors and Gaussian innovations}$ demonstrates over-rejection in finite-samples when the largest autoregressive root of the regressor is nonlocal-to-unity. An attempt of modeling innovations by a multivariate GARCH process is then made in Section $\ref{Simulation with CCC-GARCH innovations}$. This is further refined in Section $\ref{Simulation with common GARCH innovations}$ where it is hypothesized that innovation variances of both the regressor and the regressand share a common stochastic trend that is modeled by a GARCH process. Section $\ref{Simulation with common GJR-GARCH innovations}$ concludes the Monte Carlo evidence by simulation of the common stochastic trend by GJR-GARCH with conditional leptokurtosis. Empirical findings are replicated and evaluated on out-of-sample data in Section $\ref{Empirical Results}$. Finally, Section $\ref{conclusion}$ concludes.

@@

Whether $x_{t-1}$ is indeed predictive may be ascertained by evaluating the statistically significance of the $\beta$ coefficient obtained from an ordinary least squares [OLS] regression, i.e., testing the null hypothesis $H_0: \beta = 0$. A naïve approach is to perform a t-test of $\beta$. \citet{elliott1994inference}, however, show that the t-test leads to invalid inference if $x_{t}$ is persistent, i.e., if $\rho$ is close to unity, and the noise terms $u_{t}$ and $e_{t}$ are highly correlated. Since the regressor is a valuation ratio, which is a function of the stock price, and the regressand is the stock's return, which is also a function of the current price, there is strong reason to believe that $u_{t}$ and $e_{t}$ will indeed be highly (negatively) correlated. Sample correlations, $\hat{\delta}$, in Table~\vref{tab:cy_sp} will confirm this belief. It will also be seen that the regressor is highly persistent, manifested by the 90\% confidence interval for the largest autoregressive root containing unity. Hence, worry about the validity of the t-test is justified. A pretest, testing the null of the actual size of the t-test being unacceptably larger than nominal size $\alpha$ based on the joint presence of both aforementioned conditions, is explained in more detail in Section $\ref{pretest}$.

@@

\subsection{A pretest}
\label{pretest}
From Equation ($\ref{lua_t}$) it's easy to see that if $\delta = 0$, the nuisance term $\delta \frac{\tau_{c}}{\kappa_{c}}$ vanishes and the t-statistic collapses to the standard normal random variable $Z$. It therefore makes sense to test whether $\delta$ is different from zero. If it isn't, one can infer that the t-statistic is approximately standard normal and inference based on it is valid. This, however, is not the only condition in which there is no size distortion. \citet{phillips1987towards} shows that if $x_{t}$ is not persistent, $\tau_{c} / \kappa_{c}$ converges to a different standard normal random variable $Z^{\star}$. Hence the t-statistic, as a sum of two independent standard normal random variables, is likewise standard normal.

@@

Implementing the feasible Q-test, first $\hat{\beta}$ and its standard error $\operatorname{SE}(\widehat{\beta})$ are obtained by OLS estimation of Equation ($\ref{eqn:1}$). $x_{t}$ is written in its augmented Dickey-Fuller form
\begin{equation}
\Delta x_{t}=\tau+\theta x_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta x_{t-i}+e_{t},
\end{equation}
where $\psi_{i}=-\sum_{j=i}^{p-1} a_{j}$, $a(L)=L^{-1}[1-(1-\rho L) b(L)]$, and $\theta=(\rho-1) b(1)$. Estimation of $\widehat{\psi}_{i}(i=1, \ldots, p-1)$ is done via OLS where $p$ is either explicitly specified or estimated via the Bayesian information criterion [BIC].
With $\widehat{u}_{t}$ and $\widehat{e}_{t}$ being the residuals of regression (1) and (2), respectively,
\begin{align} \widehat{\sigma}_{u}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t}^{2} \\ \widehat{\sigma}_{e}^{2} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{e}_{t}^{2} \\ \widehat{\sigma}_{u e} &=\frac{1}{T-2} \sum_{t=1}^{T} \widehat{u}_{t} \widehat{e}_{t} \\ \widehat{\delta} &=\frac{\widehat{\sigma}_{u e}}{\widehat{\sigma}_{u} \widehat{\sigma}_{e}} \\ \widehat{\omega}^{2}&=\widehat{\sigma}_{e}^{2} /\left(1-\sum_{i=1}^{p-1} \widehat{\psi}_{i}\right)^{2}
\end{align}
are then computed. OLS estimation of Equation ($\ref{eqn:22}$) yields $\widehat{\rho}$ and its standard error $\mathrm{SE}(\widehat{\rho})$. The residual $\widehat{v}_{t}$ is used to compute 
\begin{equation}
\widehat{\sigma}_{v}^{2}=(T-2)^{-1} \sum_{t=1}^{T} \widehat{v}_{t}^{2}.
\end{equation} 
Now, to compute the DF-GLS statistic, $\left(x_{0}, x_{1}-\rho_{G L S} x_{0}, \ldots, x_{T}-\rho_{G L S} x_{T-1}\right)^{\prime}$ is regressed onto 
$\left(1,1-\rho_{G L S}, \ldots, 1-\rho_{G L S}\right)^{\prime}$ with $\rho_{G L S}=1-7 / T$. The coefficient $\mu_{G L S}$ is used to compute $\overline{x}_{t}=x_{t}-\mu_{G L S}$ which, in turn, is needed for the regression 
\begin{equation}
\Delta \overline{x}_{t}=\theta \overline{x}_{t-1}+\sum_{i=1}^{p-1} \psi_{i} \Delta \overline{x}_{t-i}+e_{t},
\end{equation} which is estimated with no intercept. Finally, the t-statistic for $\theta$ is computed. This is the DF-GLS statistic. To confirm that no error is conducted in this estimation procedure, the DF-GLS statistic thus obtained is compared to the implementation in the urca package of \citet{urca}.

@@

\section{Monte Carlo simulation}
This section, next to the out-of-sample results in Section $\ref{Empirical Results}$, accommodates one of the main contributions of this paper.\footnote{All code generating the Monte Carlo results is available at https://github.com/jpwoeltjen/\\PersistentRegressors/tree/master/MonteCarlo.} First, Monte Carlo evidence of \citet{campbell2006efficient} is replicated providing reassurance that both parties implemented the method correctly. Next, the Bonferroni Q-test is tested by violating key assumptions about the regressor's persistence. Furthermore, innovations are modeled by increasingly realistic distributions, for which justification in the form of real-world parameter estimates is given.
\label{Monte Carlo simulation}
\subsection{Simulation with Gaussian innovations}
\label{Simulation with Gaussian innovations}
To confirm the correct implementation of the procedure, Table~\vref{tab:cy} replicates Table 3 of \citet{campbell2006efficient} with the same input parameters. For each parameter combination, 10,000 Monte Carlo samples are drawn from a multivariate standard normal distribution with correlation $\delta$. These variates represent the innovations, which are used to simulate sample paths according to system ($\ref{eqn:1}$, $\ref{eqn:2}$). The null hypothesis $H_0: \beta = 0$ is tested against the alternative $H_1: \beta > 0$ at the 5\% significance level. If the Bonferroni confidence interval lies strictly above zero, the one-sided test is rejected. 
\begin{table}[hb!]
\caption{Finite-sample rejection rates}
\label{tab:cy}
\centering

@@

As argued by \citet{phillips2014confidence}, the feasible Q-test as derived in Section $\ref{Derivation of the tests}$ is asymptotically invalid when the largest autoregressive root of the regressor is not local-to-unity. In the following, finite-sample behavior is demonstrated as $\rho$ diverges from unity. Again, 10,000 Monte Carlo simulations are run with bivariate Gaussian innovations. A relatively small sample size is chosen to keep the DF-GLS statistic small in absolute value and thus stay in the vicinity of the implementation of \citet{campbell2005implementing}. Table~\vref{tab:non-local} shows that as $\rho$ distances itself from the unity neighborhood, the Bonferroni Q-test significantly over-rejects the true null of no predictability. Over-rejection is largest for highly correlated innovations and large $|c|$ where it surpasses 200\%.

@@

\citet{campbell2006efficient} evaluate the robustness of the Q-test under a fat-tailed distribution. In particular, they find finite-sample rejection probabilities to be unchanged from the Gaussian case when the innovations follow a Student t-distribution with five degrees of freedom. As shown by \citet{cavaliere2005unit}, unit root tests may be invalid under conditional heteroskedasticity. Assumptions in the form of Equation ($\ref{eqn:covarst}$) imply validity of the Q-test under conditionally heteroskedastic innovations only if they are covariance stationary. 

@@

Simulation is performed similar as in the CCC-GARCH model but now $h_{1, t} =h_{2, t}$ in Equation ($\ref{eqn:40}$). Results in Table~\vref{tab:cst-garch} compared with Table~\vref{tab:cy}  indicate that the one-sided Bonferroni Q-test tends to over-reject the true null if innovations are modeled as described above.
\begin{table}[hbt]
\centering
\caption{Finite-sample rejection rates (common stochastic trend)}
\label{tab:cst-garch}
\begin{threeparttable}
\begin{tabular}{rrrrrrrrrr}
  \hline
  & Obs & $c$ & $\rho$ & $\delta$ & $\alpha_{_{GARCH}}$ & $\beta_{_{GARCH}}$ & t-test &BQ& BQ$_{{2sided}}$ \\ 
  \hline
1 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.90 & 0.2815 & 0.0952 & 0.0990 \\ 
  2 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.80 & 0.2762 & 0.1009 & 0.1048 \\ 
  3 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.50 & 0.2706 & 0.0942 & 0.0977 \\ 
  4 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.40 & 0.2676 & 0.0961 & 0.1004 \\ 
  5 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.30 & 0.2628 & 0.0932 & 0.0972 \\ 
  6 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.20 & 0.2704 & 0.0908 & 0.0943 \\ 
  7 & 50 & -2 & 0.961 & -0.9500 & 0.0999 & 0.10 & 0.2677 & 0.0935 & 0.0984 \\ 
  8 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.90 & 0.3135 & 0.0733 & 0.0771 \\ 
  9 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.80 & 0.2812 & 0.0703 & 0.0771 \\ 
  10 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.50 & 0.2780 & 0.0683 & 0.0747 \\ 
  11 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.40 & 0.2797 & 0.0676 & 0.0742 \\ 
  12 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.30 & 0.2758 & 0.0664 & 0.0734 \\ 
  13 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.20 & 0.2746 & 0.0629 & 0.0703 \\ 
  14 & 100 & -2 & 0.980 & -0.9500 & 0.0999 & 0.10 & 0.2749 & 0.0656 & 0.0715 \\ 
   \hline
\end{tabular}
 \begin{tablenotes}
 \small
\item This Table displays the finite-sample rejection rates of the true null for right-tailed [BQ] and two-tailed  [BQ$_{{2sided}}$] Bonferroni Q-tests of predictability at $\alpha$=0.05 and $\alpha$=0.1, respectively, with the variances of innovations sharing a common stochastic trend which is modeled as a univariate GARCH(1, 1) process. 10,000 Monte Carlo simulations are performed.
\end{tablenotes}
\end{threeparttable}
\end{table}

\subsection{Simulation with common GJR-GARCH innovations}
\label{Simulation with common GJR-GARCH innovations}
\citet*{glosten1993relation} [GJR] observe that in financial markets, negative shocks contribute disproportionately more to future return volatility than positive shocks. To model the dynamics of real markets more adequately, innovation variances are modeled by the conditional variance of a common univariate GJR-GARCH process. This process models conditional variance as
\begin{equation}
h_{t}^{2}=\omega+\left(\alpha+\gamma S_{t-1}\right) \epsilon_{t-1}^{2}+\beta h_{t-1}^{2},
\end{equation}
where $$S_{t-1}=\left\{\begin{array}{ll}{1} & {\text { if } \epsilon_{t-1}<0} \\ {0} & {\text { if } \epsilon_{t-1} \geq 0.}\end{array}\right.$$
When $\gamma>0$, negative shocks increase volatility more than positive shocks. The GJR-GARCH process is covariance stationary if $\alpha+\gamma / 2+\beta<1$. Further, to allow for conditional leptokurtosis, $\eta_{t}$ in Equation ($\ref{eqn:garch}$) now follows a generalized error distribution with parameter $\theta$, i.e., $$\eta_{t} \stackrel{i i d}{\sim}GED(\theta).$$ Parameter estimates for monthly returns of the CRSP value weighted index from 1926 to 2003 are displayed in Table~\vref{tab:gjr-garch}. Since $\hat{\alpha}+\hat{\gamma} / 2+\hat{\beta}=0.958$ real return volatilities are close to nonstationary.
\begin{table}[!htbp] \centering 
  \caption{Parameter Estimates of the GJR-GARCH(1, 1)} 
  \label{tab:gjr-garch} 
  \begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 &  Estimate &  Rob. Std. Error &  Rob. t value & Pr(\textgreater \textbar t\textbar ) \\ 
\hline \\[-1.8ex] 
$\omega$ & $0.0001$ & $0.00004$ & $2.982$ & $0.003$ \\ 
$\alpha$ & $0.040$ & $0.025$ & $1.599$ & $0.110$ \\ 
$\beta$ & $0.861$ & $0.028$ & $30.881$ & $0.000$ \\ 
$\gamma$ & $0.114$ & $0.045$ & $2.562$ & $0.010$ \\ 
$\theta$ & $1.515$ & $0.089$ & $17.058$ & $0.000$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
 \begin{tablenotes}
 \small
\item Data is taken from Motohiro Yogo's website. Returns are the CRSP value weighted index log-returns from 1926 to 2003 minus the risk free rate.
\end{tablenotes}
\end{threeparttable}
\end{table}
Monte Carlo paths are simulated with $\omega = 0.000118$, $\gamma=0.0999$, $\theta=1.5$, $\alpha=0$ and letting $\beta$ increase to 0.95 such that the process approaches nonstationarity. The simulation outcome is displayed in Table~\vref{tab:mc_grj-garch}. It is observed that under realistic volatility modeling, the right-tailed Bonferroni Q-test tends to over-reject the true null of no predictability. Even for the larger sample size of 100, the amount of over-rejection of the right-tailed Q-test at 5\% significance level surpasses 50\%. The null for the smaller sample size is over-rejected more than 100\%. For very large sample sizes of more than 1000 observations, a single spike of over-rejection is found when the GARCH process is very near nonstationarity. Otherwise, rejection rates are close to the nominal size.

@@

For all datasets, both regressors are highly negatively correlated with returns. The confidence interval for $\rho$ is very near to unity in all cases, and containing it in some. Hence, the pretest of Section $\ref{pretest}$ indicates non-standard null distribution of the t-test for every sampling frequency and regressor, invalidating inference based on t-statistics, which otherwise would be statistically significant. Based on the Bonferroni Q-test, the null hypothesis of no predictability can be rejected at the 5\% significance level for ldp and lep at the annual sampling frequency and for all datasets, respectively. 

@@

$p$ denotes the optimal number of lags selected by BIC. pt is a boolean denoting whether the pretest of Section $\ref{pretest}$ rejects the null of actual size greater than 0.075. $CI_{\rho}$ and $CI_{\beta}$ denote the confidence interval for $\rho$ and $\beta$, respectively.
